Fleet Definitions for Georges Bank

### 2021-03-04 docs/GBFleetDefinitions.Rmd
add plot for gear types = 1% of landings (least caught)

>>>>

### Species that make up < 1% landings

```{r dendro3,out.width="100%",fig.cap="The dendrogram obtained from a nearest-neighbor, hierarchical cluster analysis on a subset of gear types in the Georges Bank Ecological Production unit as defined by statistical areas. Gear types were selected based on not contributing to top 99% of landings",eval=T,echo=F}
knitr::include_graphics("figures/dendrogram3.png")
